---
title: "Energías Renovables"
author: "Andrea Parra"
date: "04-10-2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}

library(tidyverse)
library(knitr)
library(magrittr)
library(broom)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(bookdown)
library(readxl)
energy <- read_csv("all_energy_statistics.csv")
countries <- read_csv("countries.csv")

knitr::opts_chunk$set(echo = FALSE)
```

# Hola

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

#Introducción
## Energías renovables

- Bullet 1
- Bullet 2
- Bullet 3

# Métodos
## Métodos

```{r cars, echo = TRUE}
summary(cars)
```

# Resultados
## Resultados

```{r pressure}
plot(pressure)
```

# Discusión
## Discusión

# Conclusiones
## Conclusiones

## Bibliografía